Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
removed unwanted stuff

{\color{red}
\subsection{Correctness of liveness analysis}

@@

\section{Computing liveness and its encoding as DFA}\label{sec:computing}
Section~\ref{sec:liveness} gave  a context-sensitive liveness analysis
and  {\color  {red}  proved  it  correct  with  reference  to  a  {\em
    minefield} semantics}.  In  particular, $\mathcal{L}$ and \pmap{f}
together described a liveness set for each program point in a function
in terms of  a given $\sigma$ and \Lfonly.  However,  we still have to
describe how to obtain demand transformers \Lfonly\ from the rule {\sc
  live-define} and how to compute the specific demand $\sigma$ on each
function.
%%
To  answer these  questions, it  is convenient  to cast  the equations
arising  out of  $\mathit{ref}$ and  $\mathcal{L}$ as  the rules  of a
grammar.   To do  so, we  need  to modify  the rules  themselves to  a
different form.

@@

\pagebreak

\pagebreak
\section{Appendix}

@@

%% %------------------------------------------------------------%
%% %\input{lazy-liveness}

\end{document}

>>>>

\mycomment{\color{red}
\subsection{Correctness of liveness analysis}

@@

\section{Computing liveness and its encoding as DFA}\label{sec:computing}
Section~\ref{sec:liveness} gave  a context-sensitive liveness analysis
and  \mycomment{\color  {red}  proved  it  correct  with  reference  to  a  {\em
    minefield} semantics}.  In  particular, $\mathcal{L}$ and \pmap{f}
together described a liveness set for each program point in a function
in terms of  a given $\sigma$ and \Lfonly.  However,  we still have to
describe how to obtain demand transformers \Lfonly\ from the rule {\sc
  live-define} and how to compute the specific demand $\sigma$ on each
function.
%%
To  answer these  questions, it  is convenient  to cast  the equations
arising  out of  $\mathit{ref}$ and  $\mathcal{L}$ as  the rules  of a
grammar.   To do  so, we  need  to modify  the rules  themselves to  a
different form.

@@

\mycomment{
\pagebreak
\pagebreak
\section{Appendix}

@@

%% %------------------------------------------------------------%
%% %\input{lazy-liveness}
}
\end{document}
